### 2017-03-01 doc/Thesis/data/theory.tex
Thesis: Adding IQS iteration analysis
reviewed theory chapter

To derive the amplitude equation, the shape/precursors equations are weighted by a space-dependent function and integrated over the phase-space. The weight function is typically the adjoint flux $\phi^{*g}$, which can be proven to minimize truncation error \cite{duderstadt1976nuclear}. The final expressions are given below:
\begin{subequations}
\be
\frac{dp}{dt}=\left[\frac{\rho-\bar{\beta}}{\Lambda}\right]p+\sum_{i=1}^I\bar{\lambda}_i\xi_i
\label{eq:p}
\ee
\be
\frac{d\xi_i}{dt}=\frac{\bar{\beta}_i}{\Lambda}-\bar{\lambda}_i\xi_i \quad 1 \le i \le I 
\label{eq:c}
\ee
\end{subequations}
This equation is also known as the point reactor kinetics equation (PRKE); where the reactivity, effective delayed-neutron fraction, and delayed-neutron precursor decay constant are defined as follows:
\begin{subequations}
\be
\frac{\rho-\bar{\beta}}{\Lambda} = 
\frac{ \sum_{g=1}^G\left(\phi^{*g},\frac{\chi_p^g}{\keff}(1-\beta)\sum_{g'=1}^G \nu^{g'} \Sigma_f^{g'}\varphi^{g'} + \sum_{g'\neq g}^G\Sigma_s^{g'\to g} \varphi^{g'} -\left( -\div D^g \grad  + \Sigma_r^g \right)\varphi^g\right)}
{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)}
\label{eq:rmb}
\ee
\be
\frac{\bar{\beta}}{\Lambda} = \sum_{i=1}^I\frac{\bar{\beta}_i}{\Lambda} = 
\sum_{i=1}^I\frac{1}{\keff}\frac{\sum_{g=1}^G(\phi^{*g}, \chi_{d,i}^g\beta_i\sum_{g'=1}^G\nu^{g'} \Sigma_f^{g' }\varphi^{g'})}
{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)}
\label{eq:b}
\ee
\be
\bar{\lambda}_i = \frac{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\lambda_i C_i)}{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^gC_i)}
\label{eq:l}
\ee 
\end{subequations}
The following inner product definition has been used: $\left(\phi^{*g},f\right):=\int_D\phi^{*g}(\vec{r})f(\vec{r})d^3r$.\\

@@

For simplicity, the previous section only described the IQS implementation using the neutron diffusion equation. However, deriving the IQS form for other neutron balance equations (e.g., transport, simplified transport, etc.) is very similar. To this end, we re-write the neutron conservation equations in operator form, shown in \eqt{eq:transport}. 
\be
\frac{\partial}{\partial t}\left(\frac{\Psi^g}{v^g}\right) = \sum_{g'} \left(H^{g'\to g} + P_p^{g' \to g} \right) \Psi^{g'} - L^g\Psi^g + S_d^g
\label{eq:transport}
\ee
where $\Psi^g$ is the multigroup neutron flux (angular flux in the case of transport), $H^{g'\to g}$ is the scattering operator, $P_p^{g' \to g}$ is the prompt neutron production operator, $L^g$ is the loss operator, and $S_d^g$ is the delayed neutron source operator. Using \eqt{eq:flux}, the reader may easily obtain the functional form for these operators in the case of a diffusion approximation.
%
%Factorization is defined as $\Psi^g(\vec{r},\vec{\Omega},t)=p(t)\psi^g(\vec{r},\vec{\Omega},t)$ and the resulting shape equation is defined by \eqt{eq:tshape}.  
Next, the factorization $\Psi^g(\vec{r},\vec{\Omega},t)=p(t)\psi^g(\vec{r},\vec{\Omega},t)$ is introduced, where the shape is denoted by $\psi^g$, leading to the following shape equations, \eqt{eq:tshape}:
\be
\frac{\partial}{\partial t}\left(\frac{\psi^g}{v^g}\right) = \sum_{g'} \left(H^{g' \to g} + P_p^{g' \to g}\right) \psi^{g'} - \left( L^g + \frac{1}{v^g}\frac{1}{p}\frac{dp}{dt}\right) \psi^g + \frac{1}{p} S_d^g
\label{eq:tshape}
\ee
Finally, the PRKE parameters are defined by \eqts{eq:trmb}{eq:tb}, where 
$\left(\Psi^{*g},f^g\right) =$\\ $ \int_{4\pi}\int_D \Psi^{*g}(\vec{r},\vec{\Omega})f^g(\vec{r},\vec{\Omega})d^3r d^2\Omega$.
\be
\frac{\rho-\bar{\beta}}{\Lambda}=\frac{ \sum_{g=1}^G\left(\Psi^{*g},\sum_{g'}(H^{g' \to g}g+P_p^{g' \to g}-L^{g'}\delta_{g'g})\psi^{g'}\right)}{\sum_{g=1}^G\left(\Psi^{*g},\frac{1}{v^g}\psi^g\right)}
\label{eq:trmb}
\ee
\be
\frac{\bar{\beta}}{\Lambda}=\sum_{i=1}^I\frac{\bar{\beta}_i}{\Lambda}=\sum_{i=1}^I\frac{\sum_{g=1}^G(\Psi^{*g}, \sum_{g'} P_{d,i}^{g' \to g} \psi^{g'})}{\sum_{g=1}^G\left(\Psi^{*g},\frac{1}{v^g}\psi^g\right)}
\label{eq:tb}
\ee
where $P_{d,i}^{g' \to g}$ is the delayed-neutron operator for precursor group $i$. \\
\indent This section is simply meant to show the theoretical expandability of IQS to transport problems and its derivation in operator notation.  As stated previously, this research only applies and tests IQS with diffusion problems.

@@

Where $n$ is the time step, $k$ is the iteration number, and $\epsilon_{\varphi}$ is the numerical criteria provided by a user.  There is no guarantee that the shape converges, so max number of iterations is typically enforced.

@@

In order to preserve the uniqueness criteria, it is beneficial to scale the shape such that the $K_n$ is constant, shown in \eqt{eq:shape_scale}.  This scaling can also be done after each iteration, to insure that the uniqueness criteria is satisfied whenever the shape is evaluated.
\be 
\varphi^{g}_n = \varphi^{g,(\text{last})}_n \frac{K_0}{K^{(\text{last})}_{n}}
\label{eq:shape_scale}
\ee

@@

IQS is first and foremost a nuclear reactor simulation method.  In nuclear reactors, multiple physics affect the profile of the neutron flux.  The most simple example of mulitphysics reactor simulations is adiabatic heat up with Doppler feedback. The principle of Doppler feedback is that fission in a fuel causes the material to increase temperature and induces a change in the neutronics properties.  The material heat up is described by \eqt{eq:temp}; where $\rho$ is the material density, $c_p$ is the specific heat, $T$ is temperature, and $\kappa_f$ is the energy released per fission \cite{ANL_BPB}. The change in temperature of the material mainly affects the thermal macroscopic absorption cross section described by \eqt{eq:dopp} \cite{ANL_BPB}.

@@

The couplings between temperature, amplitude, and shape are all nonlinear, so iteration processes are needed for each time scale.  The amplitude and temperature need to be iterated on the middle time scale until convergence on each temperature step.  Then another iterative process needs to occur in the shape time scale on all three variables. \fig{fig:proc} shows the programming diagram implement to execute this process. The time increment of $\Delta t/3$ for the temperature solve is arbitrary and is meant only to match \fig{fig:time}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Backward Difference Formulas}

An extension of implicit discretization is the backward difference formulas (BDF) \cite{Gear:2007}.  BDF's can increase the order of error convergence by interpolating solutions from previous time time steps. The general formula for BDF is discribed by \eqt{eq:bdf}.
\be 
\varphi_{n+1} = (IV-\Delta t A_{n+1})^{-1}\left[IV\sum_{j=0}^{k-1}\alpha_{jk}\varphi_{n-j} +
\Delta t b_{n+1}\right]
\label{eq:bdf}
\ee
Where $k$ is the order of the error convergence and $\alpha_{ij}$ are coefficients chosen such that the temporal truncation error is minimized.  The benifit of using BDF is that any order of convergence can be applied and are all unconditionally stable, so the IQS approximation can easily be validated for high order discretization.

@@

A common precursor evaluation technique is using the theta method, described in \sct{sect:theta}. Applying this to \eqt{eq:prec}:
\be
\frac{C^{n+1}-C^n}{\Delta t}=(1-\theta)\beta S_f^np^n-(1-\theta)\lambda C^n + \theta\beta S_f^{n+1}p^{n+1}-\theta\lambda C^{n+1}
\ee
Where $S_f$ is the fission source equivalent for shape ($S_f^n=(\nu\Sigma_f)^n\varphi^n$). Rearranging to solve for the precursor at the end of the time step yields
\be
C^{n+1} = \frac{1-(1-\theta)\Delta t\lambda}{1+\theta\Delta t\lambda}C^n + \frac{(1-\theta)\Delta t \beta}{1+\theta\Delta t\lambda}S_f^n p^n +  \frac{\theta\Delta t \beta}{1+\theta\Delta t\lambda}S_f^{n+1} p^{n+1}
\ee
Reporting this value of $C^{n+1}$, one can solve for the shape $\varphi^{n+1}$ as a function of $\varphi^n$ and $C^n$ (and $p^n$, $p^{n+1}$, $dp/dt|_n$ and  $dp/dt|_{n+1}$).
Once $\varphi^{n+1}$ has been determined, $C^{n+1}$ is updated.  Applying this technique to implicit discretization is done by changing the definition the fission source ($S_f^n=(\nu\Sigma_f)^n\varphi^n$) and eliminating all $p$ terms.

@@

Another technique to evaluating the precursor equation is to use a exponential operator and integrate the time derivative analytically.  Applying this operation to \eqt{eq:prec} yields:
\be
C^{n+1} =  C^n e^{-\lambda (t_{n+1} - t_n) }  + \int_{t_n}^{t_{n+1}} \beta(t') S_f(t') p(t')e^{-\lambda (t_{n+1}-t')}dt'
\label{eq:prec_an}
\ee
Again, this can be applied to implicit discretization by altering the definition of the fission source and eliminating $p$.  Because $S_f$ is not known continuously over the time step, the integration can be done using any schemet (Riemann, trapezoid, Simpson's, etc.). However, there is a very accurate representation of $p(t)$ over the macro step from the PRKE solve. In order to utilize this information, another possibility is to interpolate $S_f$ linearly over the macro step.  Such that:
\be
S_f(t) = \frac{t_{n+1}-t}{t_{n+1}-t_n}S_f^n  + \frac{t-t_n}{t_{n+1}-t_n}S_f^{n+1}  \quad t_n \le t \le t_{n+1}
\ee
Applying this to \eqt{eq:prec_an} yields:
\be
C^{n+1} = C^n e^{-\lambda \Delta t} + \left(\hat{a}_2 S_f^{n+1}+\hat{a}_1 S_f^n\right)\beta
\ee
With integration coefficients defined as:
\begin{align}
&\hat{a}_1= \int_{t_n}^{t_{n+1}}\frac{t_{n+1}-t'}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt' \\
&\hat{a}_2 = \int_{t_n}^{t_{n+1}}\frac{t'-t_n}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt'
\end{align}
The amplitude $(p)$ is included in the integration coefficient because it has been highly accurately calculated in the micro step scheme, so a piecewise interpolation (linear, cubic, etc.) between those points can be done to maximize accuracy.

@@

IQS will be made available to any action system capable of transient simulation, which includes:
\begin{itemize}
\item CFEM-Diffusion
\item DFEM-Diffusion
\item SAAF-CFEM-SN
\item SAAF-CFEM-PN
\item LS-CFEM-SN
\item DFEM-SN
\end{itemize}

>>>>

To derive the amplitude equation, the shape/precursors equations are weighted by a space-dependent function and integrated over the phase-space. The weight function is typically the adjoint flux $\phi^{*g}$, which can be proven to minimize truncation error \cite{duderstadt1976nuclear}. The final expressions are given below:
\begin{subequations}
\be
\frac{dp}{dt}=\left[\frac{\rho-\bar{\beta}}{\Lambda}\right]p+\sum_{i=1}^I\bar{\lambda}_i\xi_i
\label{eq:p}
\ee
\be
\frac{d\xi_i}{dt}=\frac{\bar{\beta}_i}{\Lambda}-\bar{\lambda}_i\xi_i \quad 1 \le i \le I 
\label{eq:c}
\ee
\end{subequations}
This equation is also known as the point reactor kinetics equation (PRKE); where the reactivity, effective delayed-neutron fraction, and delayed-neutron precursor decay constant are defined as follows:
\begin{subequations}
\be
\frac{\rho-\bar{\beta}}{\Lambda} = 
\frac{ \sum_{g=1}^G\left(\phi^{*g},\frac{\chi_p^g}{\keff}(1-\beta)\sum_{g'=1}^G \nu^{g'} \Sigma_f^{g'}\varphi^{g'} + \sum_{g'\neq g}^G\Sigma_s^{g'\to g} \varphi^{g'} -\left( -\div D^g \grad  + \Sigma_r^g \right)\varphi^g\right)}
{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)}
\label{eq:rmb}
\ee
\be
\frac{\bar{\beta}}{\Lambda} = \sum_{i=1}^I\frac{\bar{\beta}_i}{\Lambda} = 
\sum_{i=1}^I\frac{1}{\keff}\frac{\sum_{g=1}^G(\phi^{*g}, \chi_{d,i}^g\beta_i\sum_{g'=1}^G\nu^{g'} \Sigma_f^{g' }\varphi^{g'})}
{\sum_{g=1}^G\left(\phi^{*g},\frac{1}{v^g}\varphi^g\right)}
\label{eq:b}
\ee
\be
\bar{\lambda}_i = \frac{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^g\lambda_i C_i)}{\sum_{g=1}^G(\phi^{*g},\chi_{d,i}^gC_i)}
\label{eq:l}
\ee 
\end{subequations}
The following inner product definition has been used: $\left(\phi^{*g},f\right):=\int_D\phi^{*g}(\vec{r})f(\vec{r})d^3r$.\\  
\tcr{I vaguely remind something about $\bar{\lambda}$ not being so easy to obtain/derive/or conceptualize. What was that story?}

@@

For simplicity, the previous section only described the IQS implementation using the neutron diffusion equation. However, deriving the IQS form for other neutron balance equations (e.g., transport, simplified transport, etc.) is very similar. To this end, we re-write the neutron conservation equations in operator form, shown in \eqt{eq:transport}. 
\be
\frac{1}{v^g}\frac{\partial \Psi^g}{\partial t} = \sum_{g'} \left(H^{g'\to g} + P_p^{g' \to g} \right) \Psi^{g'} - L^g\Psi^g + S_d^g
\label{eq:transport}
\ee
where $\Psi^g$ is the multigroup neutron flux (angular flux in the case of transport), $H^{g'\to g}$ is the scattering operator, $P_p^{g' \to g}$ is the prompt neutron production operator, $L^g$ is the loss operator, and $S_d^g$ is the delayed neutron source operator. Using \eqt{eq:flux}, the reader may easily obtain the functional form for these operators in the case of a diffusion approximation.
%
%Factorization is defined as $\Psi^g(\vec{r},\vec{\Omega},t)=p(t)\psi^g(\vec{r},\vec{\Omega},t)$ and the resulting shape equation is defined by \eqt{eq:tshape}.  
Next, the factorization $\Psi^g(\vec{r},\vec{\Omega},t)=p(t)\psi^g(\vec{r},\vec{\Omega},t)$ is introduced, where the shape is denoted by $\psi^g$, leading to the following shape equations, \eqt{eq:tshape}:
\be
\frac{1}{v^g}\frac{\partial \psi^g}{\partial t}  = \sum_{g'} \left(H^{g' \to g} + P_p^{g' \to g}\right) \psi^{g'} - \left( L^g + \frac{1}{v^g}\frac{1}{p}\frac{dp}{dt}\right) \psi^g + \frac{1}{p} S_d^g
\label{eq:tshape}
\ee
Finally, the PRKE parameters are defined by \eqts{eq:trmb}{eq:tb}, where 
$\left(\Psi^{*g},f^g\right) =$\\ $ \int_{4\pi}\int_D \Psi^{*g}(\vec{r},\vec{\Omega})f^g(\vec{r},\vec{\Omega})d^3r d^2\Omega$.
\be
\frac{\rho-\bar{\beta}}{\Lambda}=\frac{ \sum_{g=1}^G\left(\Psi^{*g},\sum_{g'}(H^{g' \to g}g+P_p^{g' \to g}-L^{g'}\delta_{g'g})\psi^{g'}\right)}{\sum_{g=1}^G\left(\Psi^{*g},\frac{1}{v^g}\psi^g\right)}
\label{eq:trmb}
\ee
\be
\frac{\bar{\beta}}{\Lambda}=\sum_{i=1}^I\frac{\bar{\beta}_i}{\Lambda}=\sum_{i=1}^I\frac{\sum_{g=1}^G(\Psi^{*g}, \sum_{g'} P_{d,i}^{g' \to g} \psi^{g'})}{\sum_{g=1}^G\left(\Psi^{*g},\frac{1}{v^g}\psi^g\right)}
\label{eq:tb}
\ee
where $P_{d,i}^{g' \to g}$ is the delayed-neutron operator for precursor group $i$. \\
\indent This section is simply meant to show the theoretical expandability of IQS to transport problems and its derivation in operator notation.  As stated previously, this research only applies and tests IQS with diffusion problems.

@@

Where $n$ is the time step, $k$ is the iteration number, and $\epsilon_{\varphi}$ is the numerical criteria provided by a user.  There is no guarantee that the shape converges, so max number of iterations is typically enforced. \tcr{rephrase last bit}

@@

In order to preserve the uniqueness criteria, it is beneficial to scale the shape such that the $K_n$ is constant, shown in \eqt{eq:shape_scale}.  This scaling can also be done after each iteration, to insure that the uniqueness criteria is satisfied whenever the shape is evaluated.
\be 
\varphi^{g}_n = \varphi^{g,(\text{last})}_n \frac{K_0}{K^{(\text{last})}_{n}}
\label{eq:shape_scale}
\ee
\tcr{here, and before, $n$ seems to indicate the current time at which the solution is sought. I believe that later, the unknowns
will be described as being at $n+1$. this is a slight inconsistency.}

@@

IQS is first and foremost a nuclear reactor simulation method.  In nuclear reactors, multiple physics affect the profile of the neutron flux.  One of the simplest examples of mulitphysics reactor simulations is adiabatic heat up with Doppler feedback. The principle of Doppler feedback is that fission in a fuel causes the material to increase temperature and induces a change in the neutronics properties.  The material heat up is described by \eqt{eq:temp}; where $\rho$ is the material density, $c_p$ is the specific heat, $T$ is temperature, and $\kappa_f$ is the energy released per fission \cite{ANL_BPB}. The change in temperature of the material mainly affects the thermal macroscopic absorption cross section described by \eqt{eq:dopp} \cite{ANL_BPB}.

@@

The couplings between temperature, amplitude, and shape are all nonlinear, so iteration processes are needed for each time scale.  The amplitude and temperature need to be iterated on the middle time scale until convergence on each temperature step.  Then another iterative process needs to occur in the shape time scale on all three variables. \fig{fig:proc} shows the programming diagram implement to execute this process. The time increment of $\Delta t/3$ for the temperature solve is arbitrary and is meant only to match \fig{fig:time} where three temperature updates have been used as illustration.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Backward Difference Formulae}

An extension of implicit discretization is the backward difference formulae (BDF) \cite{Gear:2007}.  BDF's can increase the order of error convergence by interpolating solutions from previous time time steps. The general formula for BDF is described by \eqt{eq:bdf}.
\be 
\varphi_{n+1} = (IV-\Delta t A_{n+1})^{-1}\left[IV\sum_{j=0}^{k-1}\alpha_{jk}\varphi_{n-j} +
\Delta t b_{n+1}\right]
\label{eq:bdf}
\ee
Where $k$ is the order of the error convergence and $\alpha_{ij}$ are coefficients chosen such that the temporal truncation error is minimized.  The benefit of using BDF is that any order of convergence can be applied and are all unconditionally stable, so the IQS approximation can easily be validated for high order discretization.
\tcr{The $k$ subscript is confusing. It reads like $\alpha_{jk}$ is a matrix entry but the rest of the equation 2.35 is independent of $k$. Something is fishy.}

@@

A common precursor evaluation technique is using the theta method, described in \sct{sect:theta}. Applying this to \eqt{eq:prec}:
\be
\frac{C^{n+1}-C^n}{\Delta t}=(1-\theta)\beta S_f^np^n-(1-\theta)\lambda C^n + \theta\beta S_f^{n+1}p^{n+1}-\theta\lambda C^{n+1}
\ee
Where $S_f$ is the fission source equivalent for shape ($S_f^n=(\nu\Sigma_f)^n\varphi^n$). Rearranging to solve for the precursor at the end of the time step yields
\be
C^{n+1} = \frac{1-(1-\theta)\Delta t\lambda}{1+\theta\Delta t\lambda}C^n + \frac{(1-\theta)\Delta t \beta}{1+\theta\Delta t\lambda}S_f^n p^n +  \frac{\theta\Delta t \beta}{1+\theta\Delta t\lambda}S_f^{n+1} p^{n+1}
\label{eq:dnp_theta}
\ee
Reporting this value of $C^{n+1}$, one can solve for the shape $\varphi^{n+1}$ as a function of $\varphi^n$ and $C^n$ (and $p^n$, $p^{n+1}$, $dp/dt|_n$ and  $dp/dt|_{n+1}$).
Once $\varphi^{n+1}$ has been determined, $C^{n+1}$ is updated.  Applying this technique to implicit discretization is done by changing the definition the fission source ($S_f^n=(\nu\Sigma_f)^n\varphi^n$) and eliminating all $p$ terms.

@@

Another technique to evaluating the precursor equation is to use a exponential operator and integrate the time derivative analytically.  Applying this operation to \eqt{eq:prec} yields:
\be
C^{n+1} =  C^n e^{-\lambda (t_{n+1} - t_n) }  + \int_{t_n}^{t_{n+1}} \beta(t') S_f(t') p(t')e^{-\lambda (t_{n+1}-t')}dt'
\label{eq:prec_an}
\ee
Again, this can be applied to implicit discretization by altering the definition of the fission source and eliminating $p$.  Because $S_f$ is not known continuously over the time step, the integration can be done using any schemet (Riemann, trapezoid, Simpson's, etc.). However, there is a very accurate representation of $p(t)$ over the macro step from the PRKE solve. In order to utilize this information, another possibility is to interpolate $S_f$ linearly over the macro step.  Such that:
\be
S_f(t) = \frac{t_{n+1}-t}{t_{n+1}-t_n}S_f^n  + \frac{t-t_n}{t_{n+1}-t_n}S_f^{n+1}  \quad t_n \le t \le t_{n+1}
\ee
Applying this to \eqt{eq:prec_an} yields:
\be
C^{n+1} = C^n e^{-\lambda \Delta t} + \left(\hat{a}_2 S_f^{n+1}+\hat{a}_1 S_f^n\right)\beta
\label{eq:dnp_an}
\ee
With integration coefficients defined as:
\begin{align}
&\hat{a}_1= \int_{t_n}^{t_{n+1}}\frac{t_{n+1}-t'}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt' \\
&\hat{a}_2 = \int_{t_n}^{t_{n+1}}\frac{t'-t_n}{\Delta t}p(t')e^{-\lambda(t_{n+1}-t')}dt'
\end{align}
The amplitude $(p)$ is included in the integration coefficient because it has been highly accurately calculated in the micro step scheme, so a piecewise interpolation (linear, cubic, etc.) between those points can be done to maximize accuracy.

@@

IQS will be made available \tcr{this is a copy paste from an old report but it is no longer fully accurate, right?}
to any action system capable of transient simulation, which includes:
\begin{itemize}
\item CFEM-Diffusion
\item DFEM-Diffusion
\item SAAF-CFEM-SN
\item SAAF-CFEM-PN
\item LS-CFEM-SN
\item DFEM-SN
\end{itemize}
